---
title       : Normal distirbution
subtitle    : Simple App with Shiny
author      : Aleš Kotnik
job         : 
framework   : io2012        # {io2012, html5slides, shower, dzslides, ...}
highlighter : highlight.js  # {highlight.js, prettify, highlight}
hitheme     : tomorrow      # 
widgets     : []            # {mathjax, quiz, bootstrap}
mode        : selfcontained # {standalone, draft}
knit        : slidify::knit2slides
---

## Short desription of application

The [application](https://alesk.shinyapps.io/developing-data-products-project/) displays
the area under the normal curve given the mean and standard deviation of the curve and the cut-off value. 

```{r, echo=FALSE}
  x <- seq(75-50, 75+50, length=300)
  plot(x,dnorm(x, 75, 10), type="l", lwd=3)

  x1 <- seq(80, 105, length=300)
  polygon(c(80, x1), c(0, dnorm(x1, 75, 10)), col="skyblue") 
```

--- .class #id 

## Example usage

Suppose there is a test where results are normaly distributed with mean score 75 and standard deviation of 10 points.

You scored 80 points and you want to konw what percentage of students scored as high or higher than you.

---

## Calculate the value of your score

```{r}
mean <- 75
sdev <- 10
yourScore <- 85

betterThanYou <- pnorm(yourScore, mean, sdev)

``` 

`r sprintf("%.2f%%", betterThanYou*100)` scored the same or better than you.

---

## Modify parameters

You can modify: 

  - mean, 
  - standard devitaion,
  - how many standard deviations around the mean to display and
  - the value above which to shade the area
  
[Try it yourself!](https://alesk.shinyapps.io/developing-data-products-project/)





